### 2022-11-17 files/Overview.tex
Some additions to overview

\subsection{Eigenvalue problem}
In the first three sections, the idea of modal analysis is applied to the Timoshenko beam theory. The first section follows the work of \cite{VV06}. In this article, the authors present a method of calculating the eigenvalues and eigenfunctions. 
\textbf{General eigenvalue problem}\\
\textbf{Case $\bm {\lambda <\alpha }$}\\
\textbf{Case $\bm { \lambda =\alpha }$}\\
\textbf{Case $\bm {\lambda >\alpha }$}
\subsection{Cantilever beam}
This is an example of the application of the theory on a cantilever Timoshenko beam.
\subsubsection{Calculating the eigenvalues}
\subsubsection{Example of mode shapes}
\subsection{Free-free timoshenko beam}

This is an example of the application of the theory on a free-free Timoshenko beam.
The idea of a suspended Timoshenko is also discuss briefly.\\
In the next section, an empirical study of the Timoshenko beam is discussed. In the article \cite{SP06} the authors obtained the eigenvalues of a Timoshenko beam, by analyzing the natural frequencies of a real world beam. Their findings are compared to various theoretical models.\\
Last an example of the Timoshenko beam in application is presented. This section is a study of a technical report on a cantilever Timoshenko beam with elastic interfaces and a tip body.

@@

>>>>

\subsection{Eigenvalue problem}
In the first three sections, the idea of modal analysis is applied to the Timoshenko beam theory. The first section follows the work of \cite{VV06}. In this article, the authors present a method of calculating the eigenvalues and eigenfunctions. 
\textbf{General eigenvalue problem}\\
\textbf{Case $\bm {\lambda <\alpha }$}\\
\textbf{Case $\bm { \lambda =\alpha }$}\\
\textbf{Case $\bm {\lambda >\alpha }$}
\subsection{Cantilever beam}
This is an example of the application of the theory on a cantilever Timoshenko beam. In this example some results in \cite{VV06} is verified and examples of the mode shapes are given.\\

This is an example of the application of the theory on a free-free Timoshenko beam.In this example some results in \cite{VV06} is verified and examples of the mode shapes are given.\\

\subsection{Suspended beam model}
The idea of a suspended Timoshenko is also discuss briefly.\\

\subsection{SP06}
In the next section, an empirical study of the Timoshenko beam is discussed. In the article \cite{SP06} the authors obtained the eigenvalues of a Timoshenko beam, by analyzing the natural frequencies of a real world beam. Their findings are compared to various theoretical models.\\

\subsection{Cantilever Timoshenko beam with tip-body}
Last an example of the Timoshenko beam in application is presented. This section is a study of a technical report on a cantilever Timoshenko beam with elastic interfaces and a tip body.\\

The variational form is derived. Then the Galerkin apporximation is given and a numerical formula for calculting the solution of the problem is given as a resut of the Finite Element Method.\\

The numerical results in this section give some assurance that the model behaves as expected. The numerical results also contribute to the technical report. Various parameters are manipluated to see how the model behaves. The results are given in tables and figures.\\

\section{Finite element method}
This chapter is preparation for the last chapter in this dissertation. The finite element method is applied to a cantilever version of each of the models in this dissertation. The goal of the chapter is to get a numerical formula to solve the eigenvalue problem for each model. The Timoshenko beam model is excluded from this chapter since an exact methd is already presented in chapter 4.\\

@@

The model is assumed to have a rectangular cross-section and is in a cantilever configuration. The Galerkin approximation is derived and applying the finite element method, a numerical formula for solving the model problem is given.\\

In this numerical formula, the model problem is a system of linear equations. This system can be changed to obtain a numerical formula for teh eigenvalue problem.\\

\subsection{Three-dimensional elastic model}
Similar to above.

\subsection{Cantilever plate model}
Similar to above.

\section{Validity of cantilever beam and plate models}
\textbf{Parameters}
\subsection{Validity of the Timoshenko beam model}
\subsubsection{The models}
\subsubsection{Accuracy of the numerical eigenvalues}
\subsubsection{Comparing the shape of the eigenfunctions}
\textbf{Shapes relating to beam-type eigenvalues}\\
\textbf{Shapes relating to non-beam type eigenvalues}\\
\textbf{Shapes of the cross-section}\\
\textbf{Direct comparison of mode shapes}\\
\textbf{Remark}
\subsubsection{Comparing the eigenvalues}
\textbf{Results of [LVV09]}
\subsubsection{Comparison of the eigenvalues}
\subsection{Validity of the two-dimensional elastic model}
\subsubsection{The models}
\subsubsection{Accuracy of the numerical eigenvalues}
\subsubsection{Comparing the mode shapes}
\textbf{Mode shapes relating to beam type eigenvalues.}\\
\textbf{Mode shapes relating to non-beam type eigenvalues that are present in the two-dimensional model.}\\
\textbf{Mode shapes relating to non-beam type eigenvalues that are not present in the two-dimensional model.}
\subsubsection{Comparing the eigenvalues}
\subsubsection{$b > h$}
\subsection{Validity of the Reissner-Mindlin plate model}
\subsubsection{Comparing the mode shapes}
\subsubsection{Comparing the eigenvalues}
\section{Overview}
\subsection{Overview}
\section{Conclusion}
\subsection{Overview}
\textbf{Properties}\\
\textbf{Properties of Type One}\\
\textbf{Properties of Type Two}\\
\textbf{Properties}
\textbf{Different Research Approaches}\\
\textbf{Motivation}
\subsection{NRF Research Proposal}
\subsection{Modelling a Suspension Bridge: A Brief History}
\subsection{Modelling a suspension bridge: An Engineering Example}
\subsection{Simplified Mathematical Model for a Suspended Beam}
\subsubsection{Reference Configuration}
\subsubsection{System of Equations}
\textbf{Equations of Motion}\\
\textbf{Constitutive Equations}\\
\textbf{Dimensionless Equations}
\subsubsection{Boundary Conditions}
\subsection{Analysis of a Thermoelastic Timoshenko Beam Model}
\textbf{Dimensionless Equations}
\subsection{An Elastically Clamped Beam Model}
\textbf{Boundary Conditions}\\
\textbf{Hooke's law in two-dimensions}
